Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-08 introduction.tex

\begin{example}[Running example]
Throughout the paper we
illustrate our framework with music transcription examples: Given
a \emph{timeline} of musical events with arbitrary timestamps as input, parse it
into a structured music score. In our example, input events
are pairs $\< \eta, \tau>$ made of
a symbol $\eta \in \Sigma$, where $\Sigma$ stands for the
set of MIDI message symbols~\cite{?}
and  $\tau \in \mathbb{Q}$ is a timestamp. The output of parsing
is a representation of the sequence in
Common Western Music Notation (CWMN)~\cite{Gould11Notation}
where event symbols belong to the domain $\Delta$
of \emph{pitches} (e.g., A4, G5, etc.), temporal
information is encoded as \emph{durations} (whole \musWhole$,
$quarter, $\musQuarter$, eight $\musEighth$, etc), and notes are grouped in
high-level structures (beams, measures, tuplets). The following inputs
will be used:
\begin{enumerate}
  \item $I_1  = [ <e_1, 0.07>,<e_2, 0.72>,<e_3, 0.91>]$, over interval $[0,1[$
  \item $I_2  = [ <e_3, 1.05>,<e_4, 1.36>,<e_5, 1.71>]$, over interval $[1,2[$
\end{enumerate}
There exists many possible parsings of $I_1 \cup I_2$ in music notation, among
which
\includegraphics[scale=0.20]{pictures/score5.png}
and \includegraphics[scale=0.20]{pictures/score4.png}.  Wheighted
parsing associates a cost to each solution, and our framework
aims at selecting the best one with respect to this cost.
\endex
\end{example}

>>>>

\begin{example}[Running example]\label{ex:running}
Throughout the paper we
illustrate our framework with music transcription examples: Given
a \emph{timeline} of musical events with arbitrary timestamps as input, parse it
into a structured music score. In our example, input events
are pairs $\< \eta, \tau>$ made of
a symbol $\eta \in \Sigma$, where $\Sigma$ stands for the
set of MIDI message symbols~\cite{?}
and  $\tau \in \mathbb{Q}$ is a timestamp. The output of parsing
is a representation of the sequence in
Common Western Music Notation (CWMN)~\cite{Gould11Notation}
where event symbols belong to the domain $\Delta$
of \emph{pitches} (e.g., A4, G5, etc.), temporal
information is encoded as \emph{durations} (whole \musWhole$,
$quarter, $\musQuarter$, eight $\musEighth$, etc), and notes are grouped in
high-level structures (beams, measures, tuplets). The following inputs
will be used:
\begin{enumerate}
  \item $I_1  = [ <e_1, 0.07>,<e_2, 0.72>,<e_3, 0.91>]$, over interval $[0,1[$
  \item $I_2  = [ <e_3, 1.05>,<e_4, 1.36>,<e_5, 1.71>]$, over interval $[1,2[$
\end{enumerate}
There exists many possible parsings of $I_1 \cup I_2$ in music notation, among
which
\includegraphics[scale=0.20]{pictures/score5.png}
and \includegraphics[scale=0.20]{pictures/score4.png}.  Wheighted
parsing associates a cost to each solution, and our framework
aims at selecting the best one with respect to this cost.
\endex
\end{example}
